---
title: "bm project_update 12/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
# 文献参考
# 1: The Gender Gap in Salaries of Educational Administration Professors
# 可参考变量： 
# - academic rank 
# - years of experience as a professor
# - research productivity measures 里面的number of books written or edited(可以Publication做比较？)
# - current academic year salary
# - gender
# 
# 2. Pay Structure, Female Representation and the Gender Pay Gap among University Professors
# 可参考变量： 
# - department

# 常见： experience, rank
# 存在： publication rate, department

# 20191213 update: rank 不应该被移除，可以考虑partition做regression
```

```{r}
law_df = read_csv("./data/Lawsuit.csv") %>% 
  janitor::clean_names() %>% 
  mutate(mean_sal = (sal94 + sal95)/2) %>% 
  mutate(
    gender = as.factor(gender),
    dept = as.factor(dept),
    clin = as.factor(clin),
    cert = as.factor(cert),
    rank = as.factor(rank)
  ) %>% 
  mutate(gender = factor(gender, levels = c(0,1), labels = c("Female", "Male")),
         dept = factor(dept, levels = c(6,1,2,3,4,5), 
                       labels = c("Surgery", "Biochemistry/Molecular Biology", "Physiology", "Genetics", "Pediatrics", "Medicine")),
         clin = factor(clin, levels = c(0,1), labels = c("Primarily research emphasis", "Primarily clinical emphasis")),
         cert = factor(cert, levels = c(0,1), labels = c("not certified", "Board certified")),
         rank = factor(rank, levels = c(3,1,2), labels = c("Full professor", "Assistant", "Associate")))
```


```{r}
# transfrom mean_sal

law_df %>% 
  ggplot(aes(sample = mean_sal)) +
  stat_qq() + 
  stat_qq_line()

# try log transfromation

law_df = law_df %>% 
  mutate(log_mean_sal = log(mean_sal))

law_df %>% 
  ggplot(aes(sample = log_mean_sal)) +
  stat_qq() + 
  stat_qq_line()

law_df %>% 
  ggplot() + 
  geom_density(aes(x = log_mean_sal), color = "darkblue", fill = "lightblue")
```

now the shape is close to a bell. 

first, fit only gender in the model
```{r}
model_0 = lm(log_mean_sal~gender, data = law_df)
```

see if a variable is a confounder (lec 15, page 29; epi lec 7, page 69)

```{r dept confounder}
model_dept = lm(log_mean_sal~gender + dept, data = law_df)

summary(model_0)
summary(model_dept)

# the coefficient of gender change more than 10%: 0.38530 to 0.20521
# include in the model
```

```{r rank confd}
model_rank = lm(log_mean_sal~gender + rank, data = law_df)

summary(model_rank)

# coefficients change from 0.38530 to 0.34948, about 10% 
# also according to some literature reviews, 
# it should be included in the model
```

```{r prate confd}
model_prate = lm(log_mean_sal~gender + prate, data = law_df)

summary(model_prate)

# gender coeff change from 0.38530 to 0.251814, which is more than 10%. 
```

```{r exper confd}
model_exper = lm(log_mean_sal~gender + exper, data = law_df)

summary(model_exper)

# 0.38530 to 0.30755, more than 10%: keep in the model
```

```{r clin confd}
model_clin = lm(log_mean_sal~gender + clin, data = law_df)

summary(model_clin)

# 0.38530 to 0.33718, more than 10%, keep in the model
```

```{r}
model_cert = lm(log_mean_sal~gender + cert, data = law_df)

model_cert %>% summary()

# 0.38530 to 0.33285, more than 10%, keep in the model
```


therefore, we conclude that variables `dept`, `prate`, `clin`, `cert`, `rank` and `exper` should be included in the model as confounders, they should be included in the model to adjust for the main predictor `gender`. 

Now the model we have is: 

```{r}
model_1 = lm(log_mean_sal~gender + dept + rank + clin + cert + exper, data = law_df)
summary(model_1)
```

next we consider interaction terms. 

```{r}
inter_model = lm(log_mean_sal~gender + dept + prate + clin + cert + exper + gender*rank, data = law_df)

summary(model_1)
summary(inter_model)

anova(model_1, inter_model) %>% broom::tidy()
```

From the result, we notice that the p-value of interaction term is small. We should consider partition the data by rank. 

```{r}
ast_df = law_df %>% 
  filter(rank == "Assistant")

associate_df = law_df %>% 
  filter(rank == "Associate")

full_prof_df = law_df %>% 
  filter(rank == "Full professor")
```

```{r}
ast_model = lm(log_mean_sal~gender + dept + prate + clin + cert + exper, data = ast_df)

ast_model %>% broom::tidy()

summary(ast_model)
```

```{r}
asc_model = lm(log_mean_sal~gender + dept + prate + clin + cert + exper, data = associate_df)

summary(asc_model)
```


